Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-10-04 supplement/06_bat_data.Rmd
split by night before res patch

# filter for hour between 8pm and 5am
data_residence <- atl_filter_covariates(
  data = data_residence,
  filters = "hour > 20 | hour < 5"
)
```

>>>>

```{r}
# filter for hour between 8pm and 5am
data_residence <- atl_filter_covariates(
  data = data_residence,
  filters = c(
    "hour > 20 | hour < 5",
    "distance_roost > 1000")
)
```

### Split data by night-id

We assign a night-id to each position, i.e., the night-time spanning two calendar days. We then filter for data with a residence time > 5 minutes, as we expect that a bat stopped at a location for more than 5 minutes is likely to be foraging.

```{r}
# split data into separate nights
data_residence[, night := 1 + c(0, cumsum(diff(hour) > 12)), by = "TAG"]

# filter for residence time > 5 minutes
data_residence <- data_residence[resTime > 5, ]
```
